Individual Differences Across Visual Search Tasks

### 2017-01-20 writeup/manuscript.tex
pilot data and feature notes

The study consists of three different paradigms from the visual search literature in which strong individual differences were found \citep{nowakowsak2017, irons-leber2016, kristjansson2014}.

@@

>>>>

The study consists of three different paradigms from the visual search literature in which strong individual differences were found \citep{nowakowsak2017, irons-leber2016, kristjansson2014}.
{}
\subsubsection{A: Split-half array search}

\subsection{Planned Analysis}

@@

In order to characterise an individual's behaviour in this task, we will compute the proportion of the first $n$ fixations that were on heterogeneous (difficult) side of the stimuli, over all target absent trials\footnote{Only take correct trials?}. \cite{nowakowsak2017} demonstrated a strong correlation between an this metric (for $n=5$) and reaction times ($r=$). However, a re-analysis of their data shows that an even stronger correlation is obtained with $n=3$ (see Figure \ref{fig:nowakowskaBestN})
